Compositional equivalences based on Open pNets

### 2020-03-04 2016-Weak-FH-Bisim/WeakBisim.tex
quelques todo dans la derniere annexe
work on abstract

\begin{abstract}
  Strong bisimulation allows to compare open systems described using the pNets model.
  In practice, as happens in process algebras, it is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.

  Open pNets have a notion of \emph{synchronised actions}
  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
  in Lotos).

  We use this notion to define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties...

@@

%% \TODO{keep ?}
%% \paragraph{Variable management.}
%% The variables in each synchronisation vector are considered local:
%% for a given pNet expression, we must have fresh local variables for
%% each occurrence of a vector (i.e. each time we instantiate rule
%% \TrDeux). Similarly the state variables of each copy of a
%% given pLTS in the system, must be distinct, and those created for each
%% application of \TrDeux\ have to be fresh and all distinct. 
%% This is implemented within the open-automaton generation algorithm,
%% using name generation using a global counter as a suffix.

@@

@@

$ 1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

@@

$ 3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
  \ \forall n\ge 0$

$ WI_4(n) = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

@@

$ WI_9(n) = \openrule
         {\{\}, True, (\texttt{m1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$
\end{document}

>>>>

\begin{abstract}

Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one. There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences. Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, alowing some of the actions to be
  invisible or internal moves, and thus not simulated by the equivalent program.

pNets is a generalisation of automata that includes parameters, and hierarchical composition. Open pNets are pNets with holes, i.e. placeholders inside the hierarchical structure  that can be filled by sub-systems. Reasoning on open pNets allows us to reason on open systems.
  Open pNets have a notion of \emph{synchronised actions}
  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
  in Lotos).

This article defines bisimulation relations for the pNet model, to compare  systems described using the pNets model.
 We define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.

@@

\TODO{Check coherency, the use-case figures have been modified}
%% \TODO{keep ?}
%% \paragraph{Variable management.}
%% The variables in each synchronisation vector are considered local:
%% for a given pNet expression, we must have fresh local variables for
%% each occurrence of a vector (i.e. each time we instantiate rule
%% \TrDeux). Similarly the state variables of each copy of a
%% given pLTS in the system, must be distinct, and those created for each
%% application of \TrDeux\ have to be fresh and all distinct. 
%% This is implemented within the open-automaton generation algorithm,
%% using name generation using a global counter as a suffix.

@@

\TODO{To be updated completely}

@@

\TODO{no yet checked...:}
         $ 1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{000 \OTWeakarrow {\tau} 000}$

@@

@@

$ WI_9(n) = \openrule
         {\{\}, True, (\texttt{m1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

         \subsection{Details of the Bisimulation Checking}
         \TODO{To be added}

\end{document}
